---
title: "Stats 140SL LaTeX Assignment"
author: "Hayley Todd"
date: "October 18th, 2018"
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 3
header-includes:
- \usepackage{enumitem}
- \usepackage{graphicx}
- \usepackage{fontspec}
- \usepackage{color}
- \usepackage{amsmath ,amssymb ,amsthm}
- \setmainfont{Roboto-Regular}
- \setsansfont{RobotoCondensed-BoldItalic}
---
\newpage
#Introduction

In this document I will be showcasing my ability to use \LaTeX\ in R while also telling you about my home state of {\large Arizona} and some other R code. 

#Growing Up

In this section I will talk about growing up in Arizona, specifically my family and my animals.

##My Family

I was born in **Scottsdale** in **1997**. I have \textit{1 older brother} who went to **\textsf{Northern Arizona University}**. He is now a member of the \textit{US Air Force}. Here is a table with more information on my family.

```{r}
ournames <- c("Hayley","Chase","Ron","Suzette")
ourages <- c(21,30,70,60)
oursex <- c("F","M","M","F")
famdata <- data.frame(ournames,ourages,oursex)
library("xtable")
xtable(famdata)
```

##My Animals

I owned a bunch of rescue animals growing up. Those animals included:
\begin{enumerate}[label=(\roman*)]
\item Horses
\item Donkeys
\item Pigs
\item A Sheep
\item Dogs
\item Cats
\item **and a Llama**
\end{enumerate}

These are the animals we currently own:
\begin{itemize}[$\ast$]
\item Two dogs
\item Two cats
\end{itemize}

#About Arizona

Arizona's state flag is \textcolor{red}{red}, \textcolor{blue}{blue}, and \textcolor{yellow}{yellow}. It is shown below.
\includegraphics[width=0.5\linewidth]{arizonaflag} 

#Some R Code with a splash of Greek

Let's look at a data set in R that shows the Math scores from Texas Assessment of Academic Skills. 

```{r, echo = FALSE}
data(tli)
head(tli)
```

##Some computations

Lets find the average score among women and men.

```{r}
womentli <- subset(tli, sex == "F")
mentli <- subset(tli, sex == "M")
paste0("The average score among women was ",mean(womentli$tlimth)," and among men was ",mean(mentli$tlimth),".")
```

##Some plots

We could also plot the frequencies of scores among various races. 

```{r, echo = FALSE}
hispanictli <- subset(tli, ethnicty == "HISPANIC")
hist(hispanictli$tlimth, main = "Frequency of Scores for Hispanic Ethnicity")
```

```{r, echo = FALSE}
whitetli <- subset(tli, ethnicty == "WHITE")
hist(whitetli$tlimth, main = "Frequency of Scores for White Ethnicity")
```

```{r, echo = FALSE}
blacktli <- subset(tli, ethnicty == "BLACK")
hist(blacktli$tlimth, main = "Frequency of Scores for Black Ethnicity")
```

##A nice table

We can also observe the different means and standard deviations based on grade level.

```{r, echo = FALSE}
library(stargazer)
grade3 <- subset(tli, grade == 3)
grade4 <- subset(tli, grade == 4)
grade5 <- subset(tli, grade == 5)
grade6 <- subset(tli, grade == 6)
grade7 <- subset(tli, grade == 7)
grade8 <- subset(tli, grade == 8)

tlimeans <- c(mean(grade3$tlimth), mean(grade4$tlimth), mean(grade5$tlimth), mean(grade6$tlimth), mean(grade7$tlimth), mean(grade8$tlimth))

grades <- c(3:8)
tlidata <- data.frame(grades,tlimeans)
stargazer(tlidata, title = "Math Score Means Based on Grade Level")
```

